Synthesizing Symmetric Lenses

### 2018-07-03 papers/SymmetricLenses/main.tex
Some more comments

\subsection{Stochastic Regular Expression Entropy}
The entropy of a stochastic regular expression can be computed directly from its
syntax, when the stochastic regular expression is unambiguous and contains only
nonempty subcomponents.
\begin{center}
  \begin{tabular}{rcl}
    $\EntropyOf{s}$
    & =
    & 1\\

@@

    $\EntropyOf{\PRegexOr{\Regex}{\RegexAlt}{\Probability}}$
    & =
    & $\Probability*(\EntropyOf{\Regex} - \Log_2(\Probability)) + (1-\Probability)*(\EntropyOf{\RegexAlt} - \Log_2(1-\Probability))$\\
  \end{tabular}
\end{center}
We have proven\bcp{This is a POPL paper: Proofs of important theorems should
be included.} that this syntactic computation corresponds to the entropy of the
stochastic regular expression.

@@

\paragraph*{\ToStochastic} With stochastic DNF regular expressions and
\ToDNFRegex defined, it is easier to explain the function that converts regular
expressions into stochastic regular expressions, \ToStochastic. If $\Regex$ is a
stochastic DNF regular expression generated by \ToStochastic, then
$\ToDNFRegexOf{\Regex} = \DNFOf{(\Sequence_1,\frac{1}{n}) \DNFSep \ldots \DNFSep
  (\Sequence_n,\frac{1}{n})}$ for some sequences $\Sequence_1\ldots\Sequence_n$,
and every stochastic atom generated by \ToStochastic is
$\PRegexStar{\DNFRegex}{.8}$. In particular, $\ToDNFRegex$ generates regular
expressions whose DNF form gives equal probability to all sequences, and gives
iterations a .8 chance to continue iterating, as that gives a reasonable
distribution of strings when generating them from the regular expressions.

>>>>

\bcp{This is a POPL paper: Proofs of important theorems should
be included.  (This one might be easy enough that we can just label it as a
``Fact'' and omit the proof, or better yet we can say that the proof is straightforward.}

\subsection{Stochastic Regular Expression Entropy}
The {\em entropy} of a stochastic regular expression can be computed
directly from its syntax, when the stochastic regular expression is
unambiguous and contains only nonempty subcomponents.\bcp{What is an empty
  subcomponent?} 
\begin{center}
  \begin{tabular}{rcl}
    $\EntropyOf{s}$
    & =
    & 1\\

@@

    $\EntropyOf{\PRegexOr{\Regex}{\RegexAlt}{\Probability}}$
    & =
    & $\Probability*(\EntropyOf{\Regex} - \Log_2(\Probability)) + (1-\Probability)*(\EntropyOf{\RegexAlt} - \Log_2(1-\Probability))$\\
  \end{tabular}
\end{center}
We have proven\bcp{Again, some kind of proof is needed.} that this syntactic
computation corresponds to the entropy of the stochastic regular expression.

@@

\paragraph*{\ToStochastic} With stochastic DNF regular expressions and
\ToDNFRegex defined, it is easier to explain the function that converts regular
expressions into stochastic regular expressions, \ToStochastic. If $\Regex$ is a
stochastic DNF regular expression generated by \ToStochastic, then
$\ToDNFRegexOf{\Regex} = \DNFOf{(\Sequence_1,\frac{1}{n}) \DNFSep \ldots \DNFSep
  (\Sequence_n,\frac{1}{n})}$ for some sequences $\Sequence_1\ldots\Sequence_n$,
and every stochastic atom generated by \ToStochastic is
$\PRegexStar{\DNFRegex}{.8}$. In particular, $\ToDNFRegex$ generates regular
expressions whose DNF form gives equal probability to all sequences\bcp{Why?}, and gives
iterations a .8 chance to continue iterating, as that gives a reasonable
distribution of strings when generating them from the regular
expressions\bcp{What evaluation did we do to
  determine that it is the right value?}.
